---
title: "Assignment Week 6"
author: "Jihun Bae"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidytext)

```


# Assignment 6.1.1

Fill in the black below to produce the outcome.


1. Q6.1.1.1 

```{r Q6.1.1.1}
# Match ".a.b.c" only


str_subset(c(".a.b.c", "aabbcc", ".a.b.c.d"), c("\\.[c]$"))


```

2. Q6.1.1.2

```{r Q6.1.1.2}
# Match "$^$" only

str_subset(c("$^$", "ab$^$sfas"),"^[$]") # the hat indicates that it starts with an $

```



# Assignment 6.1.2
Using the corpus of common words in stringr::words, create regular expressions to find all words that meet the following questions.

*Use str_subset(stringr::words,             )

## Questions

1. Find all words that start with a vowel.
1. Find all words that only contain consonants. (*Hint: thinking about matching “not”-vowels.)
1. Find all words that end with "ed", but not with "eed". (e.g., “ed”, “bed”, “hundred”, “red”)
1. Find all words that end with "ing" or "ise".

	

## Answers 6.1.2
1. Q6.1.2.1
```{r Q6.1.2.1}
#Find all words that start with a vowel.

df <- stringr::words

str_subset(df,"^[aeiou]" )

```


2. Q6.1.2.2
```{r Q6.1.2.2}
#Find all words that only contain consonants. (*Hint: thinking about matching “not”-vowels.)

str_subset(df,"^[^aeiou]+$" ) # check this later like why do they use the plus sign
                              # the + sign indicates one or more


```

3. Q6.1.2.3
```{r Q6.1.2.3}
#Find all words that end with "ed", but not with "eed". (e.g., “ed”, “bed”, “hundred”, “red”)

str_subset(df,"[^e]ed$" )

#str_subset(df,"ed$" ) # checking all the words that end with eed also to make sure that the output is right



```

4. Q6.1.2.4
```{r Q6.1.2.4}
#Find all words that end with "ing" or "ise".

str_subset(df,"" ) # couldnt figue this out.


```
	



# Assignment 6.1.3
Create a regular expression that will match the following telephone numbers.

"123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351"

## Questions
1. match telephone number "123-456-7890"
1. match telephone numbers "(123)456-7890" and "(123) 456-7890"



## Answers 6.1.3
1. Q6.1.3.1
```{r Q6.1.3.1}

#match telephone number "123-456-7890"
x <- c("123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351")

str_subset(x,"[/d{3}][-][/d{3}][-][/d{4}]") # I couldnt figure out why this one wont work

str_subset(x,"[/d{3}][-]") # this one works correctly but is only half of the syntax


```

2. Q6.1.3.2
```{r Q6.1.3.2}

#match telephone numbers "(123)456-7890" and "(123) 456-7890"

x <- c("123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351")

str_subset(x, "\\(123\\)(?:4|\\s)") #ahh still have to figure out how the \\ works

str_subset(x,"[. | /d{3} | .] 7890$")


```


# Assignment 6.2
Consider the following dataset for healthcare organizations (hcodata):
How can you find the organizations with limited liability? (Hint: you should find the name of organization includes “B.V.” (or equivalent).


```{r Q6.2, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:/Users/pache/OneDrive - Erasmus University Rotterdam/Desktop/syons programming/Assignment Week6")

hcodata <- read_csv("hcodata.csv")
head(hcodata) 


str_subset(hcodata$Name,"[Vv].?$") #remmeber to access the column in this way or else it wont work. Also I didnt understand why the questuon mark is there in the regex. it translates to either one or more "." at the end. 





```

# Assignment 6.3
Extract and plot features from “titanic_train” data.

## Questions
1. Extract titles from "Names". View the first 10 rows of titles using head() function.
1. Plot the new variable "title" using ggplot2.
1. Extract Family names from "Names". View the first 10 rows of Family names using head() function.
1. Plot the 10 most frequent family names using ggplot2.



## Answers 6.3

1. Q6.3.1 (wouldng reccomenr using this peice of code, instead use the next code block)
```{r Q6.3.1, warning=FALSE, message=FALSE}
titanic_train <- read_csv("titanic_train.csv") 
head(titanic_train) #view the data

titles <- str_split(titanic_train$Name, " ") #split with spaces
head(titles) #check

o <- unlist(titles) #make it a straight line
view(o) #check

jk <- tibble() #creating a black tibble to read into

jk <- str_subset(o,"[.]$") #extracting the values and putting them into a black tibble
view(jk)
df5 <- data.frame(jk) # converting the tibble into a dataframe

freq <- count(df5, arrange(df5,decreasing = TRUE)) # tallies all the records into a tabel which can be read by a histogram
freq #check

ggplot(freq, aes(x=jk, y=n)) + geom_bar(stat='identity') # remember to use the stat identity option


# good video to watch that explains how to do this
#https://www.youtube.com/watch?v=sa-TUpSx1JA&list=LL&index=2&t=498s

```
```{r}
getwd()
# splitting each cell inside the character vector "Name"
# this will give us 891 lists words
titles <- str_split(titanic_train$Name, " ") %>%
# unlisting each list will yield (891*number_of_words_in_each_cell) words
# among them all the titles
unlist() %>%
# and we choose only those strings (titles, in this case)
# that end with "."
str_subset(., "\\.$") %>%
# and making a tibble out of them
tibble()

# changing the name of the column in the tibble
colnames(titles) = "titles"
head(titles)
```

The correct code block which should be used
```{r}

# Extract titles from "Names". View the first 10 rows of titles using head() function.

titanic_train <- read_csv("titanic_train.csv")

# head(titanic_train, 5)

titanic_df <- tibble(titanic_train) # creating a blank tibble

titanic_df <- titanic_df %>% #we are using this tibble created above
mutate(lcName = str_to_lower(Name)) # we need to sort of order the thing to en for cross use accross platforms

titanic_df <- titanic_df %>% #selecting the dataset that we want to use
mutate(title = str_extract(lcName, "(\\s)[a-zA-Z]+(?=\\.)")) # extracting the titles from the name column
head(titanic_df$title, 10) #using the dead command to display the fist 10 lines of code


```


2. Q6.3.2
```{r Q6.3.2}

# Plot the new variable "title" using ggplot2.

ggplot(data.frame(table(titanic_df$title)),aes(x=reorder(Var1, -Freq),y=Freq))+ 
  #table() uses the cross-classifying factors to build a contingency table of the counts at each combination of factor levels.
  #hmm it could be that for some reason that GGplot cannot plot the tibble therefore he converts it into a dataframe
geom_col()+
labs(title="Count of Title", x="Title",y="Count")

# it works perfects when you plot it inline. 



```

3. Q6.3.3
```{r Q6.3.3}
#Extract Family names from "Names". View the first 10 rows of Family names using head() function.

head(titles)
head(o)

ntib <- tibble()
ntib <- str_extract(titanic_train$Name,"[^,]+") # the regex reads as before the comma one or more
view(ntib)

fam_names <- str_extract(titanic_df$Name,"[a-zA-Z]^\\,") # dont use this lol fail


```

4. Q6.3.4 (fail - dont use this)
```{r Q6.3.4}
# Plot the 10 most frequent family names using ggplot2.

str(ntib)
ntib2 <- data.frame(ntib)# until here is correct as we can see the df
family <- count(ntib2, arrange(ntib2, freq, decreasing = TRUE))
family

sum(ntib)

ggplot(ntib= sort(ntib, decreasing = FALSE))+ geom_col(mapping = aes(x= "names", y= "count"))

```

Actual code block to use 
```{r}
# creating a df with the name frequencies (sorted in descenting order)
freq_fnames <- ntib %>%
count() %>%
arrange(.,freq, decreasing = TRUE)

up <- data.frame("a","b","c","f","v",
                 "g","a","k","d","b","f","f")

ggplot(up, aes(x = reorder(1, -freq), y = freq))+
geom_bar(stat = "identity")


ggplot() + geom_bar(aes(up))


freq_fnames %>%
# selecting the top 10 frequent names
slice(., 1:10) %>%
  
# and plotting them
ggplot(., aes(x = reorder(family_name, -freq), y = freq))+
geom_bar(stat = "identity")

```












