---
always_allow_html: true
title: "Assignment Week 7 Option 1"
author: "Jihun Bae"
output: pdf_document
editor_options: 
  chunk_output_type: console
---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidytext)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
# install.packages("friends")
library(friends)

```



Install “friends” package (install.packages(“friends”)). Use “friends” package and write codes for following tasks:


1. Tokenize the text and remove stop-words.
```{r  Q7.1.1}

friends # this is the dataset

tidy_friends <- friends  %>% 
  unnest_tokens(word,text) #tokenising the text 

tidy_friends <- tidy_friends %>%
  anti_join(get_stopwords()) #removing the stopwords

tidy_friends # seems correct 
```

2. Calculate word frequency.
```{r  Q7.1.2}

tidy_friends %>%  # this is the dataset that we calculated in the previous tokenisation step
  count(word, sort = TRUE) 

```

3. Make a wordcloud.
```{r  Q7.1.3}

tidy_friends %>% 
  count(word) %>%
  with(wordcloud::wordcloud(word,n,max.words = 100)) 

tidy_friends

```


4. Count the frequency of those positive and negative words. Show the most frequent positive and negative words, respectively, using head() function.
```{r Q7.1.4}
sentiment1

sentiment1 <- get_sentiments("bing") %>%
  count( sentiment == "negative") # this works but then I need to figure out how to rename the rows


sentiment2 <- get_sentiments("bing") %>%
  filter(sentiment == "negative", sort = TRUE)

head(sentiment2)


#ok so i didnt get this box and also further on from here needs to be studdied 

```


5. Visualize the frequency of positive and negative words by each character.
```{r Q7.1.5}






```
	




