---
title: "Assignment Week 6"
author: "Jihun Bae"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidytext)

```


# Assignment 6.1.1

Fill in the black below to produce the outcome.


1. Q6.1.1.1 

```{r Q6.1.1.1}
# Match ".a.b.c" only

str_subset(c(".a.b.c", "aabbcc", ".a.b.c.d"), c(           ))

```

2. Q6.1.1.2

```{r Q6.1.1.2}
# Match "$^$" only

str_subset(c("$^$", "ab$^$sfas"),              )

```



# Assignment 6.1.2
Using the corpus of common words in stringr::words, create regular expressions to find all words that meet the following questions.

*Use str_subset(stringr::words,             )

## Questions

1. Find all words that start with a vowel.
1. Find all words that only contain consonants. (*Hint: thinking about matching “not”-vowels.)
1. Find all words that end with "ed", but not with "eed". (e.g., “ed”, “bed”, “hundred”, “red”)
1. Find all words that end with "ing" or "ise".

	

## Answers 6.1.2
1. Q6.1.2.1
```{r Q6.1.2.1}

```


2. Q6.1.2.2
```{r Q6.1.2.2}


```

3. Q6.1.2.3
```{r Q6.1.2.3}


```

4. Q6.1.2.4
```{r Q6.1.2.4}


```
	



# Assignment 6.1.3
Create a regular expression that will match the following telephone numbers.

"123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351"

## Questions
1. match telephone number "123-456-7890"
1. match telephone numbers "(123)456-7890" and "(123) 456-7890"



## Answers 6.1.3
1. Q6.1.3.1
```{r Q6.1.3.1}
x <- c("123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351")

```

2. Q6.1.3.2
```{r Q6.1.3.2}
x <- c("123-456-7890", "(123)456-7890", "(123) 456-7890", "(123)5-2351")

```


# Assignment 6.2
Consider the following dataset for healthcare organizations (hcodata):
How can you find the organizations with limited liability? (Hint: you should find the name of organization includes “B.V.” (or equivalent).


```{r Q6.2, echo=FALSE, message=FALSE, warning=FALSE}
hcodata <- read_csv("hcodata.csv")
head(hcodata)


```

# Assignment 6.3
Extract and plot features from “titanic_train” data.

## Questions
1. Extract titles from "Names". View the first 10 rows of titles using head() function.
1. Plot the new variable "title" using ggplot2.
1. Extract Family names from "Names". View the first 10 rows of Family names using head() function.
1. Plot the 10 most frequent family names using ggplot2.



## Answers 6.3

1. Q6.3.1
```{r Q6.3.1, warning=FALSE, message=FALSE}
# Extract titles from "Names". View the first 10 rows of titles using head() function.

titanic_train <- read_csv("titanic_train.csv")
head(titanic_train, 5)

df1 <- str_split(titanic_train$Name," ")
df2 <- unlist(df1)  
df3 <- data.frame(str_subset(df2,"\\.$"))
df3

head(df3,10)

```

2. Q6.3.2
```{r Q6.3.2}
#plot the new variable "title" using ggplot2.

freq <- count(df3, arrange(df3, decreasing = TRUE)) #taollys up all the items before they can be plotted 
freq
colnames(freq)

ggplot(freq, aes(x= str_subset.df2.........,y=n)) + geom_bar(stat='identity') # remember to use the stat identity option ## also remember to list the column names correctly in AES. use colnames to check.

```

3. Q6.3.3
```{r Q6.3.3}
# Extract Family names from "Names". View the first 10 rows of Family names using head() function.
familynames <- tibble()
familynames <- str_extract(titanic_train$Name, "[^,]+")
familynames1 <- data.frame(familynames)

freq1 <-  count(familynames1, arrange(familynames1, decreasing = TRUE))#the trick with the count function is you have to input a data frame
freq1

colnames(freq1)

ggplot(freq1, aes(x= familynames,y=n)) + geom_bar(stat='identity') # ok so this works fine
names <- freq1[,1]
head(names,10)



```

4. Q6.3.4
```{r Q6.3.4}
# Plot the 10 most frequent family names using ggplot2

xya <- freq1 %>% arrange(desc(n))#order the names in descending order
view(xya) #check - yes it is correct
xya1 <- xya[1:10,] # selecting the first 10 rows
ggplot(xya1, aes(x= familynames,y=n)) + geom_bar(stat='identity') #plotting the first 10 rows
```













